### 2022-05-17 README.Rmd
Version 2.0.0 initial commit

`badge_custom(x = "arXiv", y = "abs/2106.10539", color = "yellow", url = "https://arxiv.org/abs/2106.10539")` 
[![R build status](https://github.com/nesscoder/fasano.franceschini.test/workflows/R-CMD-check/badge.svg)](https://github.com/nesscoder/fasano.franceschini.test/actions) 
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://lifecycle.r-lib.org/articles/stages.html)
`r badge_devel("nesscoder/fasano.franceschini.test", "blue")` 
`r badge_code_size("nesscoder/fasano.franceschini.test")`
`r badge_cran_download("fasano.franceschini.test", "grand-total", "blue")`

<!-- badges: end -->

The `fasano.franceschini.test` package is an R implementation of the 2-D Kolmogorov-Smirnov (**KS**) two-sample test as defined by Fasano and Franceschini (1987). This is a variant of the 2-D two-sample KS test as originally defined by Peacock (1983).

@@

## Example

#### Underlying Distributions Are Different

@@

#set seed for reproducible example
set.seed(123)

#create 2-D samples with the different underlying distributions
sample1Data <- data.frame(
  x = rnorm(n = 50, mean = 0, sd = 3),
  y = rnorm(n = 50, mean = 0, sd = 1)
)
sample2Data <- data.frame(
  x = rnorm(n = 50, mean = 0, sd = 1),
  y = rnorm(n = 50, mean = 0, sd = 3)
)

fasano.franceschini.test(sample1Data,sample2Data)
```

#### Underlying Distributions Are The Same

```{r}
#set seed for reproducible example
set.seed(123)

#create 2-D samples with the same underlying distributions
sample1Data <- data.frame(
  x = rnorm(n = 50, mean = 0, sd = 1),
  y = rnorm(n = 50, mean = 0, sd = 1)
)
sample2Data <- data.frame(
  x = rnorm(n = 50, mean = 0, sd = 1),
  y = rnorm(n = 50, mean = 0, sd = 1)
)

fasano.franceschini.test(sample1Data,sample2Data)
```

>>>>

`r badge_custom(x = "arXiv", y = "abs/2106.10539", color = "yellow", url = "https://arxiv.org/abs/2106.10539")` 
`r badge_cran_release("fasano.franceschini.test", "orange")`
`r badge_devel("nesscoder/fasano.franceschini.test", "blue")` 
`r badge_cran_download("fasano.franceschini.test", "grand-total", "green")`
[![R-CMD-check](https://github.com/cpuritz/fftest/workflows/R-CMD-check/badge.svg)](https://github.com/cpuritz/fftest/actions)
<!-- badges: end -->

The `fasano.franceschini.test` package is an R implementation of the multidimensional Kolmogorov-Smirnov two-sample test as defined by Fasano and Franceschini (1987).

```
Fasano, G. & Franceschini, A. (1987). A multidimensional version of the
Kolmogorov-Smirnov test. Monthly Notices of the Royal Astronomical Society,
225:155-170. doi: 10.1093/mnras/225.1.155.
```

@@

## Examples

#### Underlying distributions are the same

@@

# set seed for reproducibility
set.seed(0)

# create 2D samples from the same underlying distribution
S1 <- data.frame(x = rnorm(n = 50, mean = 0, sd = 1),
                 y = rnorm(n = 50, mean = 0, sd = 3))
S2 <- data.frame(x = rnorm(n = 100, mean = 0, sd = 1),
                 y = rnorm(n = 100, mean = 0, sd = 3))

fasano.franceschini.test(S1, S2, seed = 0)
```

#### Underlying distributions are different

```{r}
# set seed for reproducibility
set.seed(1)

# create 3D samples from different underlying distributions
S1 <- cbind(rgamma(n = 43, shape = 2),
            rpois(n = 43, lambda = 5),
            rpois(n = 43, lambda = 3.5))
S2 <- cbind(rgamma(n = 72, shape = 2),
            rpois(n = 72, lambda = 5),
            rpois(n = 72, lambda = 5))

fasano.franceschini.test(S1, S2, seed = 1)
```
